Millions of Type Errors

### 2023-09-07 programming23/paper.tex
session size

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}

@@

\begin{figure}[t]
  %% \includegraphics{img/row-distribution.pdf}
  \begin{tabular}{lrrr}
           & Files  &     Lines &    Edit Range \\
    Median &  7,678 &     3,115 &           926 \\
    Mean   & 11,911 &     6,497 &         3,680 \\
    Max    & 54,884 & 1,089,963 &     1,156,036 \\
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

@@

summary of timespan :: max 1387897376 median 845648 mean 3184317.084881936 stddev 15724745.722577972
summary of event-count :: max 6079 median 138 mean 286.5851851851852 stddev 582.5752201972966

@@

\begin{figure}[t]
  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      \begin{tabular}[t]{r@{~~}l@{~~}r}
         1,341,348 & \mnocheck{}          & [\pct{89.14}] \\
           156,883 & \mnonstrict{}        & [\pct{10.43}] \\
             6,505 & \mstrict{}           & [\pct{ 0.43}]
      \end{tabular}
      \begin{tabular}[t]{r@{~~}l@{~~}r}
           508,572 & due to module switch & [\pct{33.80}] \\
           996,164 & due to keystrokes    & [\pct{66.20}]
      \end{tabular}
    \end{tabular}
    \caption{Total telemetry records (1,504,736), analysis modes, and reason-for-sending}
    \label{f:total-records}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      \begin{tabular}[t]{lrl}
        595,137 & Type errors \\
        289,698 & in current module & [\pct{48.68}] \\
         30,924 & in edit range & [\pct{5.20}]
      \end{tabular}
      \begin{tabular}[t]{lrl}
        72,235,735 & {Forced-strict errors} \\
        37,027,281 & in current module & [\pct{51.26}] \\
         1,111,178 & in edit range & [\pct{1.54}]
      \end{tabular}
    \end{tabular}
    \caption{Type errors and forced-strict errors across all telemetry records}
    \label{f:total-tefs}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      \begin{tabular}[t]{lrl}
        313,509 & \mnocheck{}   & [\pct{90.19}] \\
         32,902 & \mnonstrict{} & [\pct{ 9.47}] \\
            545 & \mstrict{}    & [\pct{ 0.16}] \\
            642 & mixed-mode    & [\pct{ 0.18}]
      \end{tabular}
      \begin{tabular}[t]{l@{~~}ll}
        \zerowidth{Among the mixed-mode sessions:} \\
        & 341 & contain a mode upgrade \\
        & 320 & contain a mode downgrade \\
        & 512 & contain modules with different modes
      \end{tabular}
    \end{tabular}
    \caption{Total sessions (347,598), whether/how they switch analysis mode}
    \label{f:total-sessions}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \caption{TODO session size}
    \label{f:sessions-size}
  \end{subfigure}

  %% TODO out/size-dist*rktd

%% TODO power-law: event count, timespan, files lines editRange /session, 
%% ... gotta know project size

>>>>

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}

@@

\begin{figure}[t]
  %% \includegraphics{img/row-distribution.pdf}
  \begin{tabular}{l@{}r@{~}l@{}r@{~}l@{}r@{~}l}
    & Files  & &     Lines & &    Edit Range & \\
    Mean [std]   & 11,911 & \stddev{31}  &     6,497 & \stddev{22} &         3,680 & \stddev{12} \\
    Median       &  7,678 &              &     3,115 &             &          926  & \\
    Max          & 54,884 &              & 1,089,963 &             &    1,156,036  & \\
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

FILL power-law files lines editrange.
Incredible max numbers.

\begin{figure}[t]
  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll}
      \begin{tabular}[t]{r@{~~}l@{~}r}
         1,341,348 & \mnocheck{}          & [\pct{89.14}] \\
           156,883 & \mnonstrict{}        & [\pct{10.43}] \\
             6,505 & \mstrict{}           & [\pct{ 0.43}]
      \end{tabular}
      \begin{tabular}[t]{r@{~~}l@{~~}r}
           508,572 & due to module switch & [\pct{33.80}] \\
           996,164 & due to keystrokes    & [\pct{66.20}]
      \end{tabular}
    \end{tabular}
    \caption{Total telemetry records (1,504,736), analysis modes, and reason-for-sending}
    \label{f:total-records}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll} \\
      \begin{tabular}[t]{l@{~~}r@{~}l}
        595,137 & Type errors \\
        289,698 & in current module & [\pct{48.68}] \\
         30,924 & in edit range & [\pct{5.20}]
      \end{tabular}
      \begin{tabular}[t]{l@{~~}r@{~}l}
        72,235,735 & {Forced-strict errors} \\
        37,027,281 & in current module & [\pct{51.26}] \\
         1,111,178 & in edit range & [\pct{1.54}]
      \end{tabular}
    \end{tabular}
    \caption{Type errors and forced-strict errors across all telemetry records}
    \label{f:total-tefs}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}[t]{ll} \\
      \begin{tabular}[t]{l@{~~}r@{~}l}
        313,509 & \mnocheck{}   & [\pct{90.19}] \\
         32,902 & \mnonstrict{} & [\pct{ 9.47}] \\
            545 & \mstrict{}    & [\pct{ 0.16}] \\
            642 & mixed-mode    & [\pct{ 0.18}]
      \end{tabular}
      \begin{tabular}[t]{l@{~~}ll}
        \zerowidth{Among the mixed-mode sessions:} \\
        & 341 & contain a mode upgrade \\
        & 320 & contain a mode downgrade \\
        & 512 & contain modules with different modes
      \end{tabular}
    \end{tabular}
    \caption{Total sessions (347,598), whether/how they switch analysis mode}
    \label{f:total-sessions}
  \end{subfigure}

  \begin{subfigure}[t]{\columnwidth}
    \begin{tabular}{l@{}r@{~}l@{}r@{~}l} \\
                   & Time Span (sec)  &       & Record Count  \\
      Mean [std]   &     3,184 & \stddev{16}  &     286 & [583] \\
      Median       &       845 &              &     138        \\
      Max          & 1,387,897 &              &   6,079        \\
      & \includegraphics[width=0.2\columnwidth]{img/timespan-distribution.pdf}
      & & \includegraphics[width=0.2\columnwidth]{img/event-count-distribution.pdf}

    \caption{Session length in seconds and in number of records}
    \label{f:sessions-size}
  \end{subfigure}

%% TODO power-law: event count, timespan

@@

@@
